Towards Verifying the Bitcoin-S Library

### 2019-06-20 paper/paper.tex
verbatim -> lstlisting

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] Code.scala:60:3: Stainless doesn't support abstract type members
              type A
              ^^^^^^
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] Code.scala:77:33: Only literal arguments are allowed for BigInt.
              def toBigInt: BigInt = BigInt(toLong)
                                            ^^^^^^
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] Code.scala:7:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]
                                         ^^^^^^^^^^^^^^
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [Warning ] Code.scala:9:3: Could not extract tree in class: type A =
             BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
             ^^^^^^^^^^^^^^^
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] Code.scala:22:14: Unknown call to & on result (BigInt) with arguments
             List(Number.this.andMask) of type List(BigInt)
            require((result & andMask) == result,
                    ^^^^^^^^^^^^^^^^
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [Warning ] Code.scala:90:3: Could not extract tree in class: case private
             class SatoshisImpl extends Satoshis with Product with Serializable {
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [Warning ] Code.scala:51:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(
             -9223372036854775808L)), "Number was too small for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying >= -9223372036854775808L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [Warning ] Code.scala:53:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(
             9223372036854775807L)), "Number was too big for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying <= 9223372036854775807L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] checkResult$0 depends on missing dependencies: require$1.
\end{verbatim}}

@@

Stainless output:
{\footnotesize
\begin{verbatim}
  [ Error  ] inv$4 depends on missing dependencies: long2bigInt$0.
\end{verbatim}}

@@

Finally, we get some output from Stainless about the verification in the code.
{\footnotesize
\begin{verbatim}
[...]
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
[Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
[...]
[  Info  ] +  precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid  Code.scala:16:45
[...]
[  Info  ] total: 5  valid: 4  (4 from cache) invalid: 1  unknown: 0  time:  1.317
\end{verbatim}}

@@

The Stainless output again:
{\footnotesize
\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
\end{verbatim}}

@@

Stainless finds another counter example:
{\footnotesize
\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(1)
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } ->
                 Int64Impl(9223372036854775807)
\end{verbatim}}

>>>>

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] Code.scala:60:3: Stainless doesn't support abstract type members
              type A
              ^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] Code.scala:77:33: Only literal arguments are allowed for BigInt.
              def toBigInt: BigInt = BigInt(toLong)
                                            ^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] Code.scala:7:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]
                                         ^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:9:3: Could not extract tree in class: type A =
             BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
             ^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] Code.scala:22:14: Unknown call to & on result (BigInt) with arguments
             List(Number.this.andMask) of type List(BigInt)
            require((result & andMask) == result,
                    ^^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:90:3: Could not extract tree in class: case private
             class SatoshisImpl extends Satoshis with Product with Serializable {
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:51:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(
             -9223372036854775808L)), "Number was too small for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying >= -9223372036854775808L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [Warning ] Code.scala:53:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(
             9223372036854775807L)), "Number was too big for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying <= 9223372036854775807L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] checkResult$0 depends on missing dependencies: require$1.
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] inv$4 depends on missing dependencies: long2bigInt$0.
\end{lstlisting}

@@

Finally, we get some output from Stainless about the verification in the code.
\begin{lstlisting}[style=stainless]
[...]
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
[Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
[...]
[  Info  ] +  precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid  Code.scala:16:45
[...]
[  Info  ] total: 5  valid: 4  (4 from cache) invalid: 1  unknown: 0  time:  1.317
\end{lstlisting}

@@

The Stainless output again:
\begin{lstlisting}[style=stainless]
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
\end{lstlisting}

@@

Stainless finds another counter example:
\begin{lstlisting}[style=stainless]
  [Warning ] Found counter-example:
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(1)
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } ->
                 Int64Impl(9223372036854775807)
\end{lstlisting}
